Investigating Fault-Proneness Through Hotfix Commits: A Research in the Light of Different Programming Languages

### 2016-02-17 main.tex
Changed the reference to .bib file

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}
\bibitem{}
Hattori, L.P.; Lanza, M., \emph{"On the nature of commits"} in Automated Software Engineering - Workshops, 2008. ASE Workshops 2008. 23rd IEEE/ACM International Conference on , vol., no., pp.63-71, 15-16 Sept. 2008
\bibitem{}
Livshits,B.; Zimmerman,T.; \emph{"DynaMine: Finding Common Error Patterns by Mining Software Revision Histories"} in Proceedings of the 10th European software engineering conference held jointly with 13th ACM SIGSOFT international symposium on Foundations of software engineering, pp.296-305
\bibitem{}
Mockus, A.; Votta, L.G., \emph{"Identifying reasons for software changes using historic databases"} in Software Maintenance, 2000. Proceedings. International Conference on , vol., no., pp.120-130, 2000
\bibitem{}
Ratzinger,J.; Sigmund,T.; Gall,H.; \emph{"On the Relation of Refactoring and Software Defects"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp. 35-38
\bibitem{}
Hindle,A.; German,D.; Holt,R.; \emph{"What do large commits tell us?: a taxonomical study of large commits"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp.99-108
\bibitem{}
Oliva,G.; Steinmacher,I.; Wiese,I.; Aurelio,M.; \emph{"What Can Commit Metadata Tell Us About Design Degradation?"} in IWPSE 2013, Proceedings of the 2013 International Workshop on Principles of Software Evolution, pp.18-27
\bibitem{}
Phillips,S.; Sillito,J.; Walker,R.; \emph{"Branching and merging: an investigation into current version control practices"} in CHASE '11 Proceedings of the 4th International Workshop on Cooperative and Human Aspects of Software Engineering, pp.9-15
\bibitem{}
Agrawal, K.; Amreen, S.; Mockus, A., \emph{"Commit Quality in Five High Performance Computing Projects"} in Software Engineering for High Performance Computing in Science (SE4HPCS), 2015 IEEE/ACM 1st International Workshop on , vol., no., pp.24-29, 18-18 May 2015
\bibitem{}
Steff, M.; Russo, B., \emph{"Co-evolution of logical couplings and commits for defect estimation"} in Mining Software Repositories (MSR), 2012 9th IEEE Working Conference on , vol., no., pp.213-216, 2-3 June 2012
\bibitem{}
Williams,C.; Spacco,J.; \emph{"Branching and Merging in the Repository"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp.19-22
\bibitem{}
Kolassa,C.; Riehle,D.; Salim,M.; \emph{"The Empirical Commit Frequency Distribution of Open Source Projects"} in WikiSym '13, Proceedings of the 9th International Symposium on Open Collaboration, Article No.18
\bibitem{}
Ray,B.; Posnett,D.; Filkov,V.; Devanbu,P;  \emph{A Large Scale Study of Programming Languages and Code Quality"} in Github;  FSE 2014, Proceedings of the 22nd ACM SIGSOFT International Symposium on Foundations of Software Engineering, pp.155-165
\bibitem{}
Phipps,G; \emph{"Comparing Observed Bug and Productivity Rates for Java and C++" } in Software—Practice \& Experience; vol.29, issue 4, pp.345-358, April 10, 1999 
\bibitem{}
Prechelt, L., \emph{"An empirical comparison of seven programming languages"} in Computer , vol.33, no.10, pp.23-29, Oct 2000
\bibitem{}
Fourment,M.; Gillings,M.; \emph{"A comparison of common programming languages used in bioinformatics"} in BMC Bioinformatics Feb 2008
\bibitem{}
Furia,C.; Nanz,S.; \emph{"A Comparative Study of Programming Languages in Rosetta Code"} in ICSE '15, Proceedings of the 37th International Conference on Software Engineering, vol.1, pp.778-788
\bibitem{}
Iowa State University of Science and Technology,  \emph{"Boa - Mining Ultra-Large-Scale Software Repositories"}, http://boa.cs.iastate.edu/

\end{thebibliography}

>>>>

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

\bibliographystyle{abbrv}
\bibliography{hotfixes}

%\bibitem{}
%Hattori, L.P.; Lanza, M., \emph{"On the nature of commits"} in Automated Software Engineering - Workshops, 2008. ASE Workshops 2008. 23rd IEEE/ACM International Conference on , vol., no., pp.63-71, 15-16 Sept. 2008
%\bibitem{}
%Livshits,B.; Zimmerman,T.; \emph{"DynaMine: Finding Common Error Patterns by Mining Software Revision Histories"} in Proceedings of the 10th European software engineering conference held jointly with 13th ACM SIGSOFT international symposium on Foundations of software engineering, pp.296-305
%\bibitem{}
%Mockus, A.; Votta, L.G., \emph{"Identifying reasons for software changes using historic databases"} in Software Maintenance, 2000. Proceedings. International Conference on , vol., no., pp.120-130, 2000
%\bibitem{}
%Ratzinger,J.; Sigmund,T.; Gall,H.; \emph{"On the Relation of Refactoring and Software Defects"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp. 35-38
%\bibitem{}
%Hindle,A.; German,D.; Holt,R.; \emph{"What do large commits tell us?: a taxonomical study of large commits"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp.99-108
%\bibitem{}
%Oliva,G.; Steinmacher,I.; Wiese,I.; Aurelio,M.; \emph{"What Can Commit Metadata Tell Us About Design Degradation?"} in IWPSE 2013, Proceedings of the 2013 International Workshop on Principles of Software Evolution, pp.18-27
%\bibitem{}
%Phillips,S.; Sillito,J.; Walker,R.; \emph{"Branching and merging: an investigation into current version control practices"} in CHASE '11 Proceedings of the 4th International Workshop on Cooperative and Human Aspects of Software Engineering, pp.9-15
%\bibitem{}
%Agrawal, K.; Amreen, S.; Mockus, A., \emph{"Commit Quality in Five High Performance Computing Projects"} in Software Engineering for High Performance Computing in Science (SE4HPCS), 2015 IEEE/ACM 1st International Workshop on , vol., no., pp.24-29, 18-18 May 2015
%\bibitem{}
%Steff, M.; Russo, B., \emph{"Co-evolution of logical couplings and commits for defect estimation"} in Mining Software Repositories (MSR), 2012 9th IEEE Working Conference on , vol., no., pp.213-216, 2-3 June 2012
%\bibitem{}
%Williams,C.; Spacco,J.; \emph{"Branching and Merging in the Repository"} in MSR '08, Proceedings of the 2008 international working conference on Mining software repositories, pp.19-22
%\bibitem{}
%Kolassa,C.; Riehle,D.; Salim,M.; \emph{"The Empirical Commit Frequency Distribution of Open Source Projects"} in WikiSym '13, Proceedings of the 9th International Symposium on Open Collaboration, Article No.18
%\bibitem{}
%Ray,B.; Posnett,D.; Filkov,V.; Devanbu,P;  \emph{A Large Scale Study of Programming Languages and Code Quality"} in Github;  FSE 2014, Proceedings of the 22nd ACM SIGSOFT International Symposium on Foundations of Software Engineering, pp.155-165
%\bibitem{}
%Phipps,G; \emph{"Comparing Observed Bug and Productivity Rates for Java and C++" } in Software—Practice \& Experience; vol.29, issue 4, pp.345-358, April 10, 1999 
%\bibitem{}
%Prechelt, L., \emph{"An empirical comparison of seven programming languages"} in Computer , vol.33, no.10, pp.23-29, Oct 2000
%\bibitem{}
%Fourment,M.; Gillings,M.; \emph{"A comparison of common programming languages used in bioinformatics"} in BMC Bioinformatics Feb 2008
%\bibitem{}
%Furia,C.; Nanz,S.; \emph{"A Comparative Study of Programming Languages in Rosetta Code"} in ICSE '15, Proceedings of the 37th International Conference on Software Engineering, vol.1, pp.778-788
%\bibitem{}
%Iowa State University of Science and Technology,  \emph{"Boa - Mining Ultra-Large-Scale Software Repositories"}, http://boa.cs.iastate.edu/

%\end{thebibliography}
